The Hydrogen Epoch of Reionization Array (HERA)

### 2015-11-04 manuscript.tex
many edits in the spatial response section

\subsection{Spectral Response}
Figure \ref{fig:cosmos} highlights the frequency range requirement to probe the expected timescale of the epoch of reionization using the 21cm line of hydrogen as the probe.  
These limits are derived from to-date complementary probes of reionization which include measurements of
the optical depth to last scattering in the CMB, QSO spectra, Ly-$\alpha$
absorption in the spectra of quasars and gamma ray bursts and the demographics
of Ly-$\alpha$ emitting galaxies
%We show limits established by some of these techniques in
(Figure~\ref{fig:IonHist}). 
Constraints from these probes are still weak:
Ly-$\alpha$ absorption saturates at very small neutral fractions; galaxy
surveys directly constrain only the bright end of the luminosity function and
depend on an unknown escape fraction of ionizing photons to constrain
reionization; CMB measurements probe an integral quantity subject
to large degeneracies. Even when these observations are
combined into a single 95\% confidence region, the bounds remain weak.
For example, $x_{HI}$ spans almost the entire allowable range of [0,1]
at $z=8$. 21\,cm reionization experiments place much tighter constraints on ionization, with the
red band showing the forecasted 95\% confidence region derived from HERA data,
after marginalizing over astrophysical and cosmological parameters.

@@

\subsection{Spatial/Delay Response}
The spatial response provides the defining characteristics for the experiment; related to the diameter, focal length, baseline, and configuration.  The principal constraint sets the delay response of the antenna element, characterized by the magnitude and frequency of the antenna ripple response.  This was initially addressed to first order in [MEMO] and in a much more detailed way in [UPCOMING PAPERS].  Expressed simply, the delay response of the antenna must be sufficiently attenuated such that the foreground signal levels at those delays is below the expected signal strength of the EOR signal.  This sets the optics and match needs.  As discussed in [REFS], this is addressed by direct measurement and modeling of the response to the system relative to and as a function of delay time from the initial wave reception.  The expected strength of the foregrounds is modeled through the system and plotted on the same set of axes.  These two regions should be disjoint to a significance of 60 dB.

@@

The above requirements also drive the specification on the element diameter, as well as the desire to maximize sensitivity.  This means that the diameter should be something around 15m (that is, a fully filled aperture for the minimum baseline) with a short focal length.  This is revisited in Sec \ref{sec:cost}.

\subsection{Sensitivity}
sensitivity - reionization fraction 10$\sigma$ from 0.2-0.8

@@

\subsection{Cost}
\label{sec:cost}
\begin{figure}[t]
\centerline{
\includegraphics[width=7.5cm]{plots/costfigNew.png} 
}
\caption{\small Costing model for a fixed sensitivity system as a function of diameter (thick blue line and left axis) as well as the round-trip delay for 1,2 and 3 feed-vertex trips (dashed red lines and right axis).  The 60 ns spec is indicated by the horizontal dash line, and the two-trip intersection at about 14-meter is the vertical dashed line.
\label{fig:costfig}}
\end{figure}

@@

The approach used first sets a specification on the magnitude of the reflections within the dish on the delays of interest.  Reference \cite{heraMemo5} derives this to be that the reflections must be down by 60 dB on timescales greater then 60 nanoseconds.  
Next, using a feed pattern based on the existing PAPER dipole antenna and a fairly complete analytical model of a prime focus antenna, the effective area was found to be maximized for $f/D \approx 0.32$.  Figure \ref{fig:costfig} shows the vertex/feed round-trip travel times for one, two and three reflections with the 60 ns timescale indicated by the black dashed line.

>>>>

\begin{table}
\label{tab:specs}
\caption{Overview of requirements and specifications}
\begin{tabular}{| l | l | c |}\hline
Parameter & Value & Comments \\ \hline
\end{tabular}
\end{table}

\subsection{Spectral Response:  Frequency Range and Bandwidths}
Figure \ref{fig:cosmos} highlights the frequency range requirement to probe the expected timescale of the epoch of reionization using the 21cm line of hydrogen as the probe.  
These limits are derived from to-date complementary probes of reionization which include measurements of
the optical depth to last scattering in the CMB, QSO spectra, Ly-$\alpha$
absorption in the spectra of quasars and gamma ray bursts and the demographics
of Ly-$\alpha$ emitting galaxies
%We show limits established by some of these techniques in
(Figure~\ref{fig:IonHist}). 
Constraints from these probes are still weak:
Ly-$\alpha$ absorption saturates at very small neutral fractions; galaxy
surveys directly constrain only the bright end of the luminosity function and
depend on an unknown escape fraction of ionizing photons to constrain
reionization; CMB measurements probe an integral quantity subject
to large degeneracies. Even when these observations are
combined into a single 95\% confidence region, the bounds remain weak.
For example, $x_{HI}$ spans almost the entire allowable range of [0,1]
at $z=8$. 21\,cm reionization experiments place much tighter constraints on ionization, with the
red band showing the forecasted 95\% confidence region derived from HERA data,
after marginalizing over astrophysical and cosmological parameters.

@@

\subsection{Spatial/Delay Response:  Diameter and Baselines}
The spatial response provides the defining characteristics for the experiment; related to the diameter, focal length, baseline, and configuration.  The principal constraint sets the delay response of the antenna element, characterized by the magnitude and frequency of the antenna ripple response.  This was initially addressed to first order in [MEMO] and in a much more detailed way in [UPCOMING PAPERS].  Expressed simply, the delay response of the antenna must be sufficiently attenuated such that the foreground signal levels at those delays is below the expected signal strength of the EOR signal.  This sets the optics and match needs.  As discussed in [REFS], this is addressed by direct measurement and modeling of the response to the system relative to and as a function of delay time from the initial wave reception.  The expected strength of the foregrounds is modeled through the system and plotted on the same set of axes.  These two regions should be disjoint to a significance of 60 dB.

In order to do an initial design and a parametric study, the approach used first sets a specification on the magnitude of the feed/vertex reflections within the dish for 1, 2, and 3 round-trip travel delay times.  Reference \cite{heraMemo5} provides an initial estimate that the reflections must be down by 60 dB on timescales greater then 60 nanoseconds.  
Also in ref \cite{heraMemo5}, an analysis using a feed pattern based on the existing PAPER dipole antenna with a fairly complete analytical model of a prime focus antenna, the effective area was found to be maximized for $f/D \approx 0.32$.  Figure \ref{fig:costfig} shows the vertex/feed round-trip travel times for one, two and three reflections.

Interpreting these delay lines in Fig \ref{fig:costfig} is somewhat confusing, but note that the vertical color scale represents a fairly steep cost function preferring delay time-scales of less than 60 ns (ignoring the horizontal color scale, to be discussed in Sec \ref{sec:cost}).  The preliminary study requirement is to ensure that reflections are down by about 60 dB by that time-scale.  As seen by the black dashed line labelled '1' for one round-trip between the feed and vertex, for the focal ratio and diameters of interest  this reflection is always less than 60 ns, so this does not constrain the design.  For two round-trips (black solid line labelled '2'), we see that for diameters greater than 14.1m, the delay is less than 60 ns, so diameters less than this are preferred.  For three round-trips, we see that we would need antennas with diameters smaller than 9.4m.  However, cost (sec. \ref{sec:cost) and practicality issues ({\em i.e.}physically moving within the filled array) make these small diameters undesirable, so this means that we need to ensure that our system has sufficiently damped reflections for 3 reflections.  This is discussed in detail in UPCOMING PAPERS.

@@

The above requirements also drive the specification on the element diameter, as well as the desire to maximize sensitivity.  This means that the diameter should be something around 15m (that is, a fully filled aperture for the minimum baseline).

\subsection{Sensitivity:  Diameter, Number, and Configuration}
What is our requirement?

sensitivity - reionization fraction 10$\sigma$ from 0.2-0.8?

10\% estimate of neutral fraction?

@@

\subsection{Cost}
\label{sec:cost}
\begin{figure}[t]
\centerline{
\includegraphics[width=7.5cm]{plots/costfigNew.png} 
}
\caption{\small Costing model for a fixed sensitivity system as a function of diameter (thick blue line and left axis) as well as the round-trip delay for 1,2 and 3 feed-vertex trips (dashed red lines and right axis).  The 60 ns spec is indicated by the horizontal dash line, and the two-trip intersection at about 14-meter is the vertical dashed line.  SEE TEXT...
\label{fig:costfig}}
\end{figure}

@@
